A Descriptive Analysis of How Psychology Journals Handle Post-Publication

### 2024-01-05 manuscript/manuscript_NHB.Rmd
edited Abstract

---
title: "A Descriptive Analysis of How Psychology Journals Handle Post-Publication
  Critiques"
author: Whamond, A., Vazire, S., Clarke, B., Moodie, N., Schiavone, S., Thibault,
  R. T., & Hardwicke, T. E.
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  word_document: default
abstract: "Fostering critical discussion is essential to upholding the ethos of science
  as an unbiased, collaborative, and self-correcting endeavor. Journals can support
  this by offering options for post-publication critique, such as commentaries or
  letters, allowing peers to voice substantiated concerns of empirical articles. We
  provide a descriptive, cross-sectional analysis of post-publication critique policies
  and prevalence across both prominent randomly-selected and psychology journals.
  We found that 38% of prominent and 23% of randomly-selected psychology journals
  offered explicit options for post-publication critique. Length and time-to-submit
  limits were often not stated. Critique prevalence was rare with only a single event
  identified among two samples of 101 articles. Given the widespread recognition of
  the replication crisis in psychology, allowing avenues for criticisms to be voiced
  may help increase the credibility within the field. To support transparency and
  self-correction, psychology journals should offer clearly stated post-publication
  critique options and encourage their use.\n"
keywords: "post-publication critique, peer review, psychology, meta-research, journal
  policy, self-correction, scientific criticism"

>>>>

---
title: "A Descriptive Analysis of How Psychology Journals Handle Post-Publication
  Critiques"
author: Whamond, A., Vazire, S., Clarke, B., Moodie, N., Schiavone, S., Thibault,
  R. T., & Hardwicke, T. E.
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  word_document: default
abstract: "Fostering critical discussion is essential to upholding the ethos of science
  as an unbiased, collaborative, and self-correcting endeavor. Journals can support
  this by offering options for post-publication critique, such as commentaries or
  letters, allowing peers to voice substantiated concerns of empirical articles. We
  provide a descriptive, cross-sectional analysis of post-publication critique policies
  and prevalence across samples of a) 100 prominent and b) 100 randomly-selected and psychology journals.
  We found that 38% of prominent and 23% of randomly-selected psychology journals
  offered explicit critique options. Length and time-to-submit
  limits were often not stated. Critique prevalence was rare with only a single event
  identified among two samples of 101 articles. Given the widespread recognition of
  the replication crisis in psychology, allowing avenues for criticisms to be voiced
  may help increase credibility within the field. To support transparency and
  self-correction, psychology journals should offer clearly stated post-publication
  critique options and encourage their use.\n"
keywords: "post-publication critique, peer review, psychology, meta-research, journal
  policy, self-correction, scientific criticism"
